Efficient pedigree recording for fast population genetics simulation

### 2018-06-06 review-responses.tex

\begin{point}{}
``its{'}'' on page 11.
\end{point}

\reply{
    Thanks. Fixed, in two places.
}

\begin{point}{}
I appreciate the ``how does it perform in theory?'' section, but the final note
on the use of ``nedigree'' seems unnecessary. If you are going to use it (which I
do not recommend), you can justify it, otherwise drop it.
\end{point}

\reply{
    We agree that the discussion of ``nedigree'' is perhaps strictly unnecessary (as we note),
    but think that small touches like this generally improve the tone 
    and accessibility of scientific discourse,
    without obscuring the content.
    So, unless the AE objects, we'd rather keep it in.
    (And, we really do think that the field needs a better term for this concept!)
}

### 2018-06-06 forwards_paper.tex
put back in nedigree

% \paragraph{A final note:}
% in preparing this manuscript,
% we debated a number of possible terms for the embellished pedigree,
% i.e., the ``pedigree with ancestral recombination information''.
% Etymological consensus \citep{liberman2014little} has
% ``pedigree'' derived from the french ``pied de grue'' for the foot of a crane
% (whose branching pattern resembles the bifurcation of a single parent-offspring relationship).
% An analogous term for the embellished pedigree might then be \emph{nedigree},
% from ``nid de grue'',
% as the nest of a crane is a large jumble of (forking) branches.
% We thought it unwise to use this term throughout the manuscript,
% but perhaps it will prove useful elsewhere.

>>>>

\paragraph{A final note:}
in preparing this manuscript,
we debated a number of possible terms for the embellished pedigree,
i.e., the ``pedigree with ancestral recombination information''.
Etymological consensus \citep{liberman2014little} has
``pedigree'' derived from the french ``pied de grue'' for the foot of a crane
(whose branching pattern resembles the bifurcation of a single parent-offspring relationship).
An analogous term for the embellished pedigree might then be \emph{nedigree},
from ``nid de grue'',
as the nest of a crane is a large jumble of (forking) branches.
We thought it would be confusing to use this term throughout the manuscript,
but perhaps it will prove useful elsewhere.
